A Road Segment Prioritization Approach for Cycling Infrastructure

### 2021-04-19 README.Rmd
increase figure label sizes

---
title: A Road Segment Prioritization Approach for Cycling Infrastructure
date: "`r Sys.Date()`"
geometry: margin=2cm
bibliography:
  - mybibfile.bib
  - rlbibfile.bib
#linenumbers: true
numbersections: true
abstract: "Understanding the motivators and deterrents to cycling is essential for creating infrastructure that gets more people to adopt cycling as a mode of transport. This paper demonstrates a new approach to support the prioritisation of cycling infrastructure and cycling network design, accounting for cyclist preferences and the growing emphasis on 'filtered permeability' and 'Low Traffic Neighborhood' interventions internationally. The approach combines distance decay, route calculation, and network analysis methods to examine where future cycling demand is most likely to arise, how such demand could be accommodated within existing street networks, and how to ensure a fair distribution of investment. Although each of these methods has been applied to cycling infrastructure prioritisation in previous research, this is the first time that they have been combined, creating an integrated road segment prioritisation approach. The approach, which can be applied to other cities, as shown in the Appendix, is demonstrated in a case study of Manchester, resulting in cycling networks that balance directness against the need for safe and stress-free routes under different investment scenarios. A key benefit of the approach from a policy perspective is its ability to support egalitarian and cost-effective strategic cycle network planning. \\par\\textbf{Keywords:} cycling networks, low-traffic neighborhoods, routing, transport equity"
# keywords: "cycling networks, low-traffic neighborhoods, potential demand, routing"
output:
  # bookdown::github_document2:
  bookdown::pdf_document2:
  # # bookdown::word_document2:
      highlight: null   # to remove code highlighting in r chunks
      toc: false
      extra_dependencies: ["subcaption", "longtable", "float", "multirow", "placeins", "multicol"]
editor_options: 
  markdown: 
    wrap: 72
# elsevier style for referencing (from https://github.com/citation-style-language/styles)
csl: elsevier-harvard.csl
---

@@

```{r desirefacetcycling, fig.cap="Current and potential cycling demand", out.width="60%", fig.pos="H", fig.align="center", echo=FALSE}
knitr::include_graphics("data/Manchester/Plots/desire_facet_cycling.png")
```

@@

```{r boxplotcircuity, fig.cap="Effect of banning cyclists from trunk and primary roads for all OD pairs (Manchester)", out.width="35%", fig.show='hold', fig.align="center", echo=FALSE}
knitr::include_graphics("data/Manchester/Plots/boxplot_weighted_unweighted_distances.png")
```

@@

```{r cyclinghistmanc, fig.cap="Cycling commuting distance - Manchester (2011 census data)", out.width="30%", fig.show='hold', fig.align = "center", echo=FALSE}
knitr::include_graphics("data/Manchester/Plots/histogram_distance_cycling.png")
```

@@

```{r communitiesmanchester, fig.cap="Communities based on potential cycling demand between MSOAs (Manchester)", out.width="75%", fig.show='hold', fig.align = "center", echo=FALSE}
knitr::include_graphics("data/Manchester/Plots/communities_alternative_Manchester.png")
```
\  
<!-- this prevents text from floating above figure -->

@@

```{r growthtotal, fig.cap="Comparing overall (dashed) and community level person-km satisfied (Manchester)", out.width="35%", fig.show='hold', fig.align = "center", echo=FALSE}
knitr::include_graphics(c(
  "data/Manchester/Plots/Growth_Results/growth_utilitarian_satisfied_km_both_flow_column.png",
  "data/Manchester/Plots/Growth_Results/growth_egalitarian_satisfied_km_both_flow_column.png"
))
```

@@

```{r growth3MapandBar, fig.cap="Road segment priority (left), disaggregated by road type (right) - egalitarian growth", out.width="35%", fig.show='hold', fig.align="center", echo=FALSE}
knitr::include_graphics(c(
  "data/Manchester/Plots/Growth_Results/growth_egalitarian_priority_all_FLOW.png",
  "data/Manchester/Plots/Growth_Results/growth_egalitarian_investment_highways_flow.png"
))
```

@@

```{r componentsandGCC, fig.cap="Network characteristics", out.width="30%", fig.show='hold', fig.pos="H", fig.align = "center", echo=FALSE}
knitr::include_graphics(c(
  "data/Manchester/Plots/Growth_Results/growth_util_egal_components_number_comparisonManchester.png",
  "data/Manchester/Plots/Growth_Results/growth_util_egal_components_gcc_comparisonManchester.png"
))
```

>>>>

---
title: A Road Segment Prioritization Approach for Cycling Infrastructure
#date: "`r Sys.Date()`"
geometry: margin=2cm
bibliography:
  - mybibfile.bib
  - rlbibfile.bib
#linenumbers: true
numbersections: true
abstract: "Understanding the motivators and deterrents to cycling is essential for creating infrastructure that gets more people to adopt cycling as a mode of transport. This paper demonstrates a new approach to support the prioritisation of cycling infrastructure and cycling network design, accounting for cyclist preferences and the growing emphasis on 'filtered permeability' and 'Low Traffic Neighborhood' interventions internationally. The approach combines distance decay, route calculation, and network analysis methods to examine where future cycling demand is most likely to arise, how such demand could be accommodated within existing street networks, and how to ensure a fair distribution of investment. Although each of these methods has been applied to cycling infrastructure prioritisation in previous research, this is the first time that they have been combined, creating an integrated road segment prioritisation approach. The approach, which can be applied to other cities, as shown in the Appendix, is demonstrated in a case study of Manchester, resulting in cycling networks that balance directness against the need for safe and stress-free routes under different investment scenarios. A key benefit of the approach from a policy perspective is its ability to support egalitarian and cost-effective strategic cycle network planning. \\par\\textbf{Keywords:} cycling networks, low-traffic neighborhoods, routing, transport equity"
# keywords: "cycling networks, low-traffic neighborhoods, potential demand, routing"
output:
  # bookdown::github_document2:
  bookdown::pdf_document2:
  # # bookdown::word_document2:
      highlight: null   # to remove code highlighting in r chunks
      toc: false
      extra_dependencies: ["subcaption", "longtable", "float", "multirow", "placeins", "multicol"]
editor_options: 
  markdown: 
    wrap: 72
# elsevier style for referencing (from https://github.com/citation-style-language/styles)
csl: elsevier-harvard.csl
---

@@

```{r desirefacetcycling, fig.cap="Current and potential cycling demand", out.width="65%", fig.pos="H", fig.align="center", echo=FALSE}
knitr::include_graphics("data/Manchester/Plots/desire_facet_cycling.png")
```

@@

```{r boxplotcircuity, fig.cap="Effect of banning cyclists from trunk and primary roads for all OD pairs (Manchester)", out.width="50%", fig.show='hold', fig.align="center", echo=FALSE}
knitr::include_graphics("data/Manchester/Plots/boxplot_weighted_unweighted_distances.png")
```

@@

```{r cyclinghistmanc, fig.cap="Cycling commuting distance - Manchester (2011 census data)", out.width="40%", fig.show='hold', fig.align = "center", echo=FALSE}
knitr::include_graphics("data/Manchester/Plots/histogram_distance_cycling.png")
```

@@

```{r communitiesmanchester, fig.cap="Communities based on potential cycling demand between MSOAs (Manchester)", out.width="80%", fig.show='hold', fig.align = "center", echo=FALSE}
knitr::include_graphics("data/Manchester/Plots/communities_alternative_Manchester.png")
```
\  
<!-- this prevents text from floating above figure -->

@@

```{r growthtotal, fig.cap="Comparing overall (dashed) and community level person-km satisfied (Manchester)", out.width="48%", fig.show='hold', fig.align = "center", echo=FALSE}
knitr::include_graphics(c(
  "data/Manchester/Plots/Growth_Results/growth_utilitarian_satisfied_km_both_flow_column.png",
  "data/Manchester/Plots/Growth_Results/growth_egalitarian_satisfied_km_both_flow_column.png"
))
```

@@

```{r growth3MapandBar, fig.cap="Road segment priority (left), disaggregated by road type (right) - egalitarian growth", out.width="45%", fig.show='hold', fig.align="center", echo=FALSE}
knitr::include_graphics(c(
  "data/Manchester/Plots/Growth_Results/growth_egalitarian_priority_all_FLOW.png",
  "data/Manchester/Plots/Growth_Results/growth_egalitarian_investment_highways_flow.png"
))

@@

```{r componentsandGCC, fig.cap="Network characteristics", out.width="85%", fig.show='hold', fig.pos="H", fig.align = "center", echo=FALSE}
# knitr::include_graphics(c(
#   "data/Manchester/Plots/Growth_Results/growth_util_egal_components_number_comparisonManchester.png",
#   "data/Manchester/Plots/Growth_Results/growth_util_egal_components_gcc_comparisonManchester.png"
# ))
knitr::include_graphics("data/Manchester/Plots/Growth_Results/growth_util_egal_components_gcc_components_together_Manchester.png")
